Selecting customers

### 2021-10-31 main.Rmd
cleaning folder

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE)
# Make sure you have the latest version of rmarkdown and bookdown
#devtools::install_github("rstudio/rmarkdown")
#devtools::install_github("rstudio/bookdown")
library(ggplot2)
library(gravitas)
library(gracsr)
library(ggdendro)
library(dplyr)
library(readr)
library(visdat)
library(ggplot2)
library(tidyverse)
library(naniar)
library(here)
library(tsibble)
library(knitr)
library(patchwork)
library(GGally)
library(distributional)
library(viridis)
```

```{r external, include = FALSE, cache = FALSE}
knitr::read_chunk(here('script/smart_meter.R'))
```

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
# knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE)
# Make sure you have the latest version of rmarkdown and bookdown
#devtools::install_github("rstudio/rmarkdown")
#devtools::install_github("rstudio/bookdown")
options("knitr.graphics.auto_pdf" = TRUE,
    tinytex.verbose = FALSE)
library(knitr)
opts_chunk$set(
 echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
 fig.path = "figure/", fig.align = "center", fig.show = "hold",
 cache = TRUE, cache.path = "cache/",
 out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

```{r external, include = FALSE, cache = FALSE}
knitr::read_chunk('script/smart_meter.R')
```

```{r load-lib}

### 2021-10-31 supplementary/prototype_selection/check_with3anchors.Rmd
cleaning folder

```{r mytheme}
theme_characterisation <- function() {

  theme_bw() + # seeting theme
    theme(strip.text = element_text(size = 9,
                                    margin = margin(b = 0, t = 0))) + # narrow facet space
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + # no axis ticks 
  theme(panel.spacing =unit(0, "lines")) +  # to ensure no gap between facets
    theme(axis.text.x = element_text(angle=90, hjust=1, size = 9)) + # rotate the x-axis text
    theme(legend.position = "bottom")+
  theme(plot.margin = margin(0, 0, 0, 0, "cm")) +
  theme(axis.text.x = element_text(size=5))
}
```

```{r anchor}
anchor1 <- 11156027
anchor2 <- 10420683
anchor3 <- 8629763
anchor4 <- 11013154
kopt <- 4 # number of clusters
```

@@

@@

data_pick_one <- c(8618759, 8291696, 10357256, 8290374) %>% as_tibble
data_pick_two <- c(9044864, 8642053, 10534367, 9021526,11162275) %>% as_tibble
data_pick_three <- c(8221762, 8273636, 10359424, 8232822)%>% as_tibble
data_pick_four <- c(10590714,8495194,8589936, 8454235) %>% as_tibble

data_pick_cust <- bind_rows(
data_pick_one, data_pick_two, data_pick_three,data_pick_four,
.id = "design")

@@

@@

total_distance <- filtered_distance %>% 
mutate(total = wkndwday + moy + hod) 
#mutate(total = hod)

@@

data_heatmap_wkndwday %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, 
                  group=customer_id, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group))) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))
```

@@

p1 <- data_heatmap_wkndwday %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6)  +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))

@@

combined <- hod_group + moy_group + wkndwday_group & theme(legend.position = "bottom")
combined + plot_layout(guides = "collect")

@@

parcoord <- GGally::ggparcoord(data_pcp ,
                   columns = 3:ncol(data_pcp),
                   groupColumn = "group",
                   showPoints = FALSE, 
                   alphaLines = 0.8,
                   order = "anyClass",
                   scale = "globalminmax"
) + theme_characterisation()+
  ylab("wpd") + scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) + theme_light()
```

@@

hod_group_wpd <- data_heatmap_hod_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=group,
                  fill = as.factor(group), alpha = 0.5),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=group, 
                color = as.factor(group)), size = 1)+
  facet_wrap(~group, 
             scales = "free_y",  
             nrow = 4) + 
              #labeller = labeller(xfacet = c(`1` = "Group 2", `2` = "Group 4",`3` = "Group 1",`4` = "Group 3"))
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + 
  ylab("demand (in Kwh)") + 
  theme_light()+ 
  theme_characterisation() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1)

@@

moy_group_wpd <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") + 
  theme_light()+ 
  theme_characterisation() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) 
```

@@

wkndwday_group_wpd <- data_heatmap_wkndwday_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)+
    #theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) 
    xlab("wknd-wday") + 
  ylab("demand (in Kwh)") + 
  theme_light()+ 
  theme_characterisation() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1)

@@

wkndwday_group_wpd <- wkndwday_data%>% 
  ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
  lvplot::geom_lv(aes(fill = as.factor(group), color = as.factor(group)), k=5, alpha = 0.5) +
  #geom_boxplot(aes(fill = as.factor(group), color = as.factor(group)),alpha = 0.5)+
  #geom_boxplot(outlier.shape = NA) + 
  coord_cartesian(ylim = ylim1*1.05)+
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)   + 
  theme_light()+ 
  theme_characterisation() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) 
```

@@

combined <- hod_group_wpd + moy_group_wpd + wkndwday_group_wpd & theme(legend.position = "bottom")
combined + plot_layout(guides = "collect")

>>>>

```{r mytheme}
theme_characterisation <- function() {
theme_bw() + 
      theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) +  + theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  theme(panel.spacing =unit(0, "lines")) + 
    theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm")) +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00"))+
  theme(legend.position = "bottom")
}
```

```{r anchor}
anchor1 <- 11156027
anchor2 <- 10420683
anchor3 <- 8629763
#anchor4 <- 11013154
kopt <- 3 # number of clusters
```

@@

data_pick_one <- nn_pick_function(anchor1)
data_pick_two <- nn_pick_function(anchor2)
data_pick_three <- nn_pick_function(anchor3)
#data_pick_four <- nn_pick_function(anchor4)

@@

data_pick_cust <- bind_rows(
data_pick_one, data_pick_two, data_pick_three,
#data_pick_four,
.id = "design")

@@

```{r mds-plots}

data_pick_char <- data_pick_cust %>% 
  rename("customer_id" = "value") %>% 
  mutate(customer_id = as.character(customer_id))

mds_all <- read_rds(here("data/mds_all.rds"))  %>% 
  left_join(data_pick_char)

highlight_df <- mds_all %>% filter(customer_id %in% data_pick_char$customer_id)

total_plot <- ggplot(mds_all,
aes(x = mds1.total, y = mds2.total)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.total, y = mds2.total, color = as.factor(design)))

wpd_plot <- ggplot(mds_all,
aes(x = mds1.wpd, y = mds2.wpd)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.wpd, y = mds2.wpd, color = as.factor(design)))

hod_plot <- ggplot(mds_all,
aes(x = mds1.hod, y = mds2.hod)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.hod, y = mds2.hod, color = as.factor(design)))

moy_plot <- ggplot(mds_all,
aes(x = mds1.moy, y = mds2.moy)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.moy, y = mds2.moy, color = as.factor(design)))

wkndwday_plot <- ggplot(mds_all,
aes(x = mds1.wkndwday, y = mds2.wkndwday)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x =  mds1.wkndwday, 
                 y =  mds2.wkndwday, 
                 color = as.factor(design)))

p <- (total_plot + wpd_plot)/(hod_plot + moy_plot + wkndwday_plot)

p +
  plot_layout(guides = "collect")

@@

total_distance <- filtered_distance %>% 
mutate(total = wkndwday/2 + moy/12 + hod/24) 
#mutate(total = hod)

@@

data_heatmap_wkndwday %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, 
                  group=customer_id, 
              fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6)  +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))
```

@@

p1 <- data_heatmap_wkndwday %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6)+
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))

@@

combined <- hod_group + moy_group + wkndwday_group & theme(legend.position = "bottom")
combined + plot_layout(guides = "collect") + theme(legend.position = "bottom")

@@

parcoord <- GGally::ggparcoord(data_pcp ,
                   columns = 3:ncol(data_pcp),
                   groupColumn = "group",
                   showPoints = FALSE, 
                   alphaLines = 0.8,
                   order = "anyClass",
                   scale = "globalminmax"
) + 
  ylab("wpd") + scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) + theme_light()
```

@@

hod_group_wpd <- data_heatmap_hod_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=group,
                  fill = as.factor(group), alpha = 0.5),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=group, 
                color = as.factor(group)), size = 1)+
  facet_wrap(~group, 
             scales = "free_y",  
             nrow = 4) + 
              #labeller = labeller(xfacet = c(`1` = "Group 2", `2` = "Group 4",`3` = "Group 1",`4` = "Group 3"))
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + 
  ylab("demand (in Kwh)") + 
  theme_light() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1)

@@

moy_group_wpd <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") + 
  theme_light() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) 
```

@@

wkndwday_group_wpd <- data_heatmap_wkndwday_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)+
    #theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) 
    xlab("wknd-wday") + 
  ylab("demand (in Kwh)") + 
  theme_light() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1)

@@

wkndwday_group_wpd <- wkndwday_data%>% 
  ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
  lvplot::geom_lv(aes(fill = as.factor(group), color = as.factor(group)), k=5, alpha = 0.5) +
  #geom_boxplot(aes(fill = as.factor(group), color = as.factor(group)),alpha = 0.5)+
  #geom_boxplot(outlier.shape = NA) + 
  coord_cartesian(ylim = ylim1*1.05)+
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)   + 
  theme_light() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) 
```

@@

combined <- hod_group_wpd + moy_group_wpd + wkndwday_group_wpd & theme(legend.position = "bottom")
combined + plot_layout(guides = "collect") + theme(legend.position = "bottom")

### 2021-10-31 supplementary/prototype_selection/check_work_nqt.Rmd
cleaning folder

```{r anchor}
anchor1 <- 11156027
anchor2 <- 10420683
anchor3 <- 8629763
anchor4 <- 11013154
kopt <- 4 # number of clusters
```

@@

wkndwday <- read_rds(here("data/dist_gran_wkndwday_356cust_robust.rds"))

moy <- read_rds(here("data/dist_gran_moy_356cust.rds"))

hod <- read_rds(here("data/dist_gran_hod_356cust_robust.rds"))

@@

mds_all <- read_rds(here("data/mds_all.rds"))  %>% 
  left_join(data_pick_char)

@@

total_plot <- ggplot(mds_all,
aes(x = mds1.total, y = mds2.total)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.total, y = mds2.total, color = as.factor(design)), size = 2)

wpd_plot <- ggplot(mds_all,
aes(x = mds1.wpd, y = mds2.wpd)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.wpd, y = mds2.wpd, color = as.factor(design)), size = 2)

hod_plot <- ggplot(mds_all,
aes(x = mds1.hod, y = mds2.hod)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.hod, y = mds2.hod, color = as.factor(design)), size = 2)

moy_plot <- ggplot(mds_all,
aes(x = mds1.moy, y = mds2.moy)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.moy, y = mds2.moy, color = as.factor(design)), size = 2)

wkndwday_plot <- ggplot(mds_all,
aes(x = mds1.wkndwday, y = mds2.wkndwday)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x =  mds1.wkndwday, 
                 y =  mds2.wkndwday, 
                 color = as.factor(design)),
             size = 2)

>>>>

```{r anchor}
anchor1 <- 8302280 # 1Q
anchor2 <- 8640717  # 2Q
anchor3 <- 8402996 # 3Q
anchor4 <- 8308172 # 4Q
kopt <- 4 # number of clusters
```

@@

wkndwday <- read_rds(here("data/dist_gran_wkndwday_356cust_nqt.rds")) %>% broom::tidy()

moy <- read_rds(here("data/dist_gran_moy_356cust_nqt.rds")) %>% broom::tidy()

hod <- read_rds(here("data/dist_gran_hod_356cust_nqt.rds")) %>% broom::tidy()

@@

mds_all <- read_rds(here("data/mds_all_nqt.rds"))  %>% 
  left_join(data_pick_char)

@@

total_plot <- ggplot(mds_all,
aes(x = mds1.total, y = mds2.total)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.total, y = mds2.total, color = as.factor(design)))

wpd_plot <- ggplot(mds_all,
aes(x = mds1.wpd, y = mds2.wpd)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.wpd, y = mds2.wpd, color = as.factor(design)))

hod_plot <- ggplot(mds_all,
aes(x = mds1.hod, y = mds2.hod)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.hod, y = mds2.hod, color = as.factor(design)))

moy_plot <- ggplot(mds_all,
aes(x = mds1.moy, y = mds2.moy)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.moy, y = mds2.moy, color = as.factor(design)))

wkndwday_plot <- ggplot(mds_all,
aes(x = mds1.wkndwday, y = mds2.wkndwday)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x =  mds1.wkndwday, 
                 y =  mds2.wkndwday, 
                 color = as.factor(design)))
